### 2013-06-18 Tex/chapters/model.tex
todo Notiz

\subsection{Critical Temperature $T_c$ and Critical Exponents}
\label{ssec:finitesize}
    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    To accomplish the collapse in an semi-automatic and reproduceable
    way with an error estimate, the programm
    \texttt{autoscale.py} \cite{autoscale2009} is used.

    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
                    with cubic splines (the errorbars are too small to see)
                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                }
        \label{fig:binder_fit_s_0}
    \end{figure}
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
    is in good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\

>>>>

\subsection{Critical Temperature $T_c$ and Critical Exponents}
\label{ssec:finitesize}
    The searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklaerung: was sind beta, gamma, nu]
    To accomplish the collapse in an semi-automatic and reproduceable
    way with an error estimate, the programm
    \texttt{autoscale.py} \cite{autoscale2009} is used.
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
                    with cubic splines (the errorbars are too small to see)
                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                }
        \label{fig:binder_fit_s_0}
    \end{figure}\\
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27 k_{B}\). For
    the sake of simplicity let the Boltzmann constant \(k_{B}=1\) in the
    following.
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\),
    which is in good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
    Because \(T_{c}\) is dependend on \(J\) and hence also on the count
    of bounds, the values of \(T_{c}\) will be normalized by the mean
    sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
